Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-06 Manuscript.Rmd
Saving the new search space criteria and updated the labels within the manuscript for the meta-analysis

# This version is literally what I had selected originally, plus 25, OFC, 10v. This replicates the 7m finding. 
# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
Yeo_labels <- c("L_25_",
                "L_OFC_",
                "L_10v_",
                "R_PGi_ROI",
                "R_PGs_ROI",
                "R_8Ad_ROI",
                "R_9p_ROI",
                "R_23d_ROI",
                "R_d23ab_RO",
                "R_31a_ROI",
                "R_31pv_ROI",
                "R_31pd_ROI",
                "R_7m_ROI",
                "R_v23ab_RO",
                "R_p24_ROI",
                "R_d32_ROI",
                "R_9m_ROI",
                "R_p32_ROI",
                "R_a24_ROI",
                "R_10r_ROI",
                "R_10d_ROI",
                "L_PGi_ROI",
                "L_PGs_ROI",
                "L_8Ad_ROI",
                "L_9p_ROI",
                "L_23d_ROI",
                "L_d23ab_RO",
                "L_31a_ROI",
                "L_31pv_ROI",
                "L_31pd_ROI",
                "L_7m_ROI",
                "L_v23ab_RO",
                "L_p24_ROI",
                "L_d32_ROI",
                "L_9m_ROI",
                "L_p32_ROI",
                "L_a24_ROI",
                "L_10r_ROI",
                "L_10d_ROI",
                "R_TE1a_ROI",
                "R_STSva_RO",
                "R_s32_ROI",
                "R_9a_ROI",
                "L_p10p_ROI",
                "L_PCV_ROI")

@@

# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
allStudies <- c(studyList_sv, studyList_dmn)
nPerms <- 100
nullDist <- numeric()

>>>>

# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
# Minus PGi and PGs. This replicates the 7m finding. 
# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
Yeo_labels <- c("L_25_ROI",
                "L_OFC_ROI",
                "L_10v_ROI",
                "R_25_ROI",
                "R_OFC_ROI",
                "R_10v_ROI",
                "L_s32_ROI",
                "L_RSC_ROI",
                "R_RSC_ROI",
                "R_8Ad_ROI",
                "R_9p_ROI",
                "R_23d_ROI",
                "R_d23ab_ROI",
                "R_31a_ROI",
                "R_31pv_ROI",
                "R_31pd_ROI",
                "R_7m_ROI",
                "R_v23ab_ROI",
                "R_p24_ROI",
                "R_d32_ROI",
                "R_9m_ROI",
                "R_p32_ROI",
                "R_a24_ROI",
                "R_10r_ROI",
                "R_10d_ROI",
                "L_8Ad_ROI",
                "L_9p_ROI",
                "L_23d_ROI",
                "L_d23ab_RO",
                "L_31a_ROI",
                "L_31pv_ROI",
                "L_31pd_ROI",
                "L_7m_ROI",
                "L_v23ab_ROI",
                "L_p24_ROI",
                "L_d32_ROI",
                "L_9m_ROI",
                "L_p32_ROI",
                "L_a24_ROI",
                "L_10r_ROI",
                "L_10d_ROI",
                "R_s32_ROI",
                "R_9a_ROI",
                "L_p10p_ROI",
                "L_PCV_ROI")

@@

# For each permutation, reassign the study labels, maintaining the original number of studies per condition 
allStudies <- c(studyList_sv, studyList_dmn)
nPerms <- 5000
nullDist <- numeric()
